### 2018-08-03 ANA-TOPQ-2017-07-PAPER-metadata.tex
some fixes to text

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.4}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed searching for top quark pair events in which one top quark decays to $Wb$ and the other top quark decays to $Hq$,
and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ interactions measured so far.
}

>>>>

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.4}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed searching for top quark pair events in which one top quark decays to $Wb$ and the other top quark decays to $Hq$,
and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ interactions measured so far.
}

### 2018-08-03 sections/data_presel.tex
some fixes to text

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
For ditau triggers, the threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

@@

Events selected by the $\Htautau$ search are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1--2~\gev. In addition, its electric charge is required to be of
opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both channels at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and sub-leading $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

@@

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking period). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both channels at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and sub-leading $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2018-08-03 sections/introduction.tex
Implemented some CDS comments from Michele Weber
some fixes to text

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark, with a 
measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
In the Standard Model (SM), such decays are extremely suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher-orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
On the other hand, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
See Ref.~\cite{AguilarSaavedra:2004wm} for a review.
\textbf{Update a bit above paragraph mentioning more recent models.}

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of $\ttbar$ events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. In contrast, multilepton searches are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
signatures with two same-charge light leptons (electrons or muons) or three light leptons resulting from 
$H \to WW^*$, $H\to \tau\tau$ in which both leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. On the other hand, the CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.

@@

The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
Therefore, they help complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on proton-proton collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 
and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.

>>>>

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark, with a 
measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
In the Standard Model (SM), such decays are extremely suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher-orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
On the other hand, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
See Ref.~\cite{AguilarSaavedra:2004wm} for a review.
%\textbf{Update a bit above paragraph mentioning more recent models.}

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of $\ttbar$ events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. In contrast, multilepton searches are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
signatures with two same-charge light leptons (electrons or muons) or three light leptons resulting from 
$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. On the other hand, the CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.

@@

The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
Therefore, they help complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on proton-proton collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 
and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.

### 2018-08-03 sections/objects.tex
some fixes to text

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
the sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

@@

Hadronically decaying $\tau$-lepton candidates ($\tauhad$) are reconstructed from clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of 1. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for the purpose of background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

Overlaps between candidate objects are removed sequentially, following this order: muons, electron, taus (only for the $\Htautau$ search) and jets. 
In the $\Hbb$ search, firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon 
candidate are removed to suppress contributions from muon bremsstrahlung.  Overlaps between electron and jet candidates are resolved 
next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
Clusters from identified electrons are not excluded during jet reconstruction.
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If 
the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
In the $\Htautau$ search, a fixed cone size of $\Delta R = 0.2$ is used to determine the overlap between candidate objects, and only the
highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the analysis channel, see Section~\ref{sec:data_presel}) are considered 
to resolve their overlap with jets. 
%firstly, the electron within a ${\Delta}R = 0.2$ cone of muons are excluded, then the $\tau_{had}$'s or jets within a ${\Delta}R = 0.2$ cone of an electron or muon are excluded. Finally, the jets within a ${\Delta}R = 0.2$ cone of the leading $\had$ ($\lephad$), or with the two leading $\had$’s ($\hadhad$) are excluded.

>>>>

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
the sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

@@

Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for the purpose of background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

Overlaps between candidate objects are removed sequentially, following this order: muons, electrons, $\tauhad$ (only for the $\Htautau$ search), and jets. 
In the $\Hbb$ search, firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon 
candidate are removed to suppress contributions from muon bremsstrahlung.  Overlaps between electron and jet candidates are resolved 
next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
Clusters from identified electrons are not excluded during jet reconstruction.
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If 
the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
In the $\Htautau$ search, a fixed cone size of $\Delta R = 0.2$ is used to determine the overlap between candidate objects, and only the
highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the analysis channel, see Section~\ref{sec:data_presel}) are considered 
to resolve their overlap with jets. 
%firstly, the electron within a ${\Delta}R = 0.2$ cone of muons are excluded, then the $\tau_{had}$'s or jets within a ${\Delta}R = 0.2$ cone of an electron or muon are excluded. Finally, the jets within a ${\Delta}R = 0.2$ cone of the leading $\had$ ($\lephad$), or with the two leading $\had$’s ($\hadhad$) are excluded.
